### 2017-06-16 manuscript/manuscript.Rmd
Add R Studio screenshots.

Managing projects (and Git repositories) with R Studio is centered on the idea of R Projects. To start a new project with R Studio, open the R Studio application, and click File -> New Project. This brings up a dialog asking whether to create a project in a new directory, existing directory, or checkout an existing project from a version control repository. Here, we create a new project in a new directory, and choose "New Project" in the following screen. Then we'll give a name to the project's home folder and choose where to save it on the computer. Importantly, we'll also check the "Create a git repository" box, which will automatically set up a new repository for the project (provided you have set Git up as detailed above). Clicking "Create project" creates the folder in the specified location, and two files inside the project's main folder.

```{r rstudio-project-1, fig.cap = "Creating a project in R Studio."}
knitr::include_graphics("images/rstudio-project-1.png")
```

>>>>

Managing projects (and Git repositories) with R Studio is centered on the idea of R Projects. To start a new project with R Studio, open the R Studio application, and click File -> New Project. This brings up a dialog (left panel in Figure \@ref(fig:rstudio-project-1)) asking whether to create a project in a new directory, existing directory, or checkout an existing project from a version control repository. Here, we create a new project in a new directory, and choose "New Project" in the following screen (middle panel in Figure \@ref(fig:rstudio-project-1)). Then we'll give a name to the project's home folder and choose where to save it on the computer. Importantly, we'll also check the "Create a git repository" box (right panel in Figure \@ref(fig:rstudio-project-1)), which will automatically set up a new repository for the project (provided you have set Git up as detailed above). Clicking "Create project" creates the folder in the specified location, and two files inside the project's main folder.

```{r rstudio-project-1, fig.cap = "Creating a project in R Studio.", out.width="6in"}
knitr::include_graphics("images/rstudio-project-1.png")
```
